Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-05-25 WholePlotTrajectories.Rmd
Graphs

```{r Options, echo=FALSE, message=FALSE, warning=F}
knitr::opts_chunk$set(cache=F, warning=F, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library("kableExtra")
source("Scripts/DrawingTools.R")
#source("Scripts/GithubPages.R")
```

@@

The impact of disturbance was examined specifically through the linear correlation between the intial %AGB removed and the Simpson and Rao diversities (diversities of order 2) after 10, 20 and 30 years \@ref(fig:IDHplot).
The correlation with disturbance intensity was weak for the Simpson diversity ($R^2<0.25$) and only valid from 20 years after disturbance but it was much stronger for the Rao diversity ($0.55<R^2<0.75$) for all the time studied.
Slope of linear correlations, reflecting the impact of disturbance, was the highest 20 years after disturbance.

>>>>

```{r Options, echo=FALSE, message=FALSE, warning=F}
knitr::opts_chunk$set(cache=F, warning=F, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library("kableExtra")

source("Scripts/DrawingTools.R")
#source("Scripts/GithubPages.R")
```

@@

The impact of disturbance was examined specifically through the linear correlation between the intial %AGB removed and the Simpson and Rao diversities (diversities of order 2) after 10, 20 and 30 years \@ref(fig:IDHplot).
The correlation with disturbance intensity was weak for the Simpson diversity ($R^2<0.25$) and only valid from 20 years after disturbance but it was much stronger for the Rao diversity ($0.60<R^2<0.75$) for all the time studied.
Slope of linear correlations, reflecting the impact of disturbance, was the highest 20 years after disturbance.
